Automating Verification of MPC Security: $\metaprot$ to $\minifed$

### 2023-07-11 popl24/ygc.tex
add quotes ygc.tex

\begin{fpfig}{Yao's Garbled Circuits, selected auxiliary functions.}{fig-ygc-aux}
{\footnotesize
\begin{verbatimtab}
  keygen(gid, b1, b2) { select4(b1,b2,H[gid || 1],H[gid || 2],H[gid || 3],H[gid || 4]) }

@@

  sharetable(gid, tid, table)
  {   
    v[1, gate: || gid || tid || 1] := table.v1;
    v[1, gate: || gid || tid || 2] := table.v2;
    v[1, gate: || gid || tid || 3] := table.v3;
    v[1, gate: || gid || tid || 4] := table.v4
  }

@@

\begin{fpfig}{Yao's Garbled Circuits, garbled gates and evaluation code.}{fig-ygc-gates}
{\footnotesize
\begin{verbatimtab}
  garbledecode(gid)    
  {
    let wl = owl(gid) in
    let r1 = wl.k xor true in
    let r0 = (not wl.k) xor false in
    v[1,OUTtt1] := select(wl.p,r1,r0);
    v[1,OUTtt2] := select(not wl.p,r1,r0)
  }

  evaldecode(wv) { wv.k xor select(wv.p,v[1,OUTtt1],v[1,OUTtt2]) }

  evalgate(gid, wva, wvb)  
  {
    let k = keygen(gid,wva.k,wvb.k) in
    let g = gate: || gid in
    let ct = select4(wva.p,wvb.p,
               v[1,g || tt1],v[1,g || tt2],v[1,g || tt3],v[1,g || tt4]) in
    let cp = select4(wva.p,wvb.p,
               v[1,g || pt1],v[1,g || pt2],v[1,g || pt3],v[1,g || pt4]) in
    { k = k xor ct; p = k xor cp }
  }

>>>>

\begin{fpfig}{Yao's Garbled Circuits, selected auxiliary functions.}{fig-ygc-aux}
{\footnotesize
\begin{verbatimtab}
  keygen(gid, b1, b2) { select4(b1,b2,H[gid || "1"],H[gid || "2"],H[gid || "3"],H[gid || "4"]) }

@@

  sharetable(gid, tid, table)
  {   
    v[1, gate: || gid || tid || "1"] := table.v1;
    v[1, gate: || gid || tid || "2"] := table.v2;
    v[1, gate: || gid || tid || "3"] := table.v3;
    v[1, gate: || gid || tid || "4"] := table.v4
  }

@@

\begin{fpfig}{Yao's Garbled Circuits, garbled gates and evaluation code.}{fig-ygc-gates}
{\footnotesize
\begin{verbatimtab}
  garbledecode(gid)    
  {
    let wl = owl(gid) in
    let r1 = wl.k xor true in
    let r0 = (not wl.k) xor false in
    v[1,"OUTtt1"] := select(wl.p,r1,r0);
    v[1,"OUTtt2"] := select(not wl.p,r1,r0)
  }

  evaldecode(wv) { wv.k xor select(wv.p,v[1,"OUTtt1"],v[1,"OUTtt2"]) }

  evalgate(gid, wva, wvb)  
  {
    let k = keygen(gid,wva.k,wvb.k) in
    let g = gate: || gid in
    let ct = select4(wva.p,wvb.p,
               v[1,g || "tt1"],v[1,g || "tt2"],v[1,g || "tt3"],v[1,g || "tt4"]) in
    let cp = select4(wva.p,wvb.p,
               v[1,g || "pt1"],v[1,g || "pt2"],v[1,g || "pt3"],v[1,g || "pt4"]) in
    { k = k xor ct; p = k xor cp }
  }
